---
title: "Introduction to the binomial package"
author: "Vincent Le"
date: "4/30/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```



##Introduction to the "binomial" package
The "binomial" package is intended to automate some of the calculations of the binomial distribution. Ultimately, it is a very basic package, and provides a minimal coverage of the options one can take with the binomial distribution.


##Basic functions
Using `bin_choose()`, one can find the number of combinations in which k successes can happen in n trials. For example, the number of combinations for 2 successes (two tails) in 10 trials (ten flips of a coin) can be given by:

```{r}
bin_choose(10, 2)
```

\n
Note that `bin_choose()` is on its own not very impressive, and isn't really tied to the binomial distribution in  a very concrete way. `bin_probability()` invokes the binomial probability equation. To get the probability of flipping 2 heads and 8 tails for a fair coin one would input:
```{r}
bin_probability(success = 2, trials = 10, prob = 0.5)
```

Note that `bin_probability()` also allows for the calculation of multiple success scenarios:
```{r}
#probability of 1, 2, or 3 heads in 10 flips
bin_probability(success = 1:3, trials = 10, prob = 0.5)
```

\n

##The Binomial Distribution 
If we wanted to look at the entire distribution, one would use `bin_distribution()`, which take arguments `trials` and `prob`, and returns a data frame with number of success in one column and probability in the other:
```{r}
#distribution given 10 trials, with a 0.5 chance of success
bin_distribution(trials = 10, prob = 0.5)
```
One can easily plot this distribution by assigning the output of `bin_distribution()` to a variable, and then calling `plot()`:

```{r}
bindis_plot <- bin_distribution(trials = 10, prob = 0.5)
plot(bindis_plot)
```

\n

##The Binomial Cumulative Distribution 
If we want to look at the cumulative probabilities, we can use `bin_cumulative()`, which takes in the same arguments as `bin_distribution()` and returns a nearly identical data frame - except this time, with a third column that includes cumulative probabilities:
```{r}
bin_cumulative(trials = 10, prob = 0.5)
```
Again, this can be easily plotted with `plot()`.
```{r, fig.show='hold'}
bincum_plot <- bin_cumulative(trials = 10, prob = 0.5)
plot(bincum_plot)

```

\n

##The Binomial Random Variable
The binomial package also allows the user to create a binomial random variable and then easily calculate summary statistics. To create the binomial variable, use `bin_variable()`:
```{r}
bin_variable(trials = 10, prob = 0.3)
```
One can then take the `summary()` of the binomial variable to access the summary statistics, such as mean, variance, mode, skewness, or kurtosis:
```{r}
bin_var <- bin_variable(trials = 10, prob = 0.3)
summary(bin_var)
```

\n

##Summary functions
If the user only wants specific descriptive statistics, the binomial package also includes separate functions for each of the summary statistics provided in `bin_variable()`:
```{r}
#mean
bin_mean(trials = 10, prob = 0.3)

#variance
bin_variance(trials = 10, prob = 0.3)

#mode
bin_mode(trials = 10, prob = 0.3)

#skewness
bin_skewness(trials = 10, prob = 0.3)

#kurtosis
bin_kurtosis(trials = 10, prob = 0.3)

```

